---
title: "GSE299686 Reanalysis"
format: gfm
---

```{r}
#| include: False
here::i_am("README.qmd")
```

# Introduction
This repository contains the source code for my reanalysis of the GSE299686 dataset, involving response of mice cancer models to anti-PD-1 treatment. 

# Prerequisites
Make sure the following are installed on your system:  

- Quarto
- R 4.5.1

# Reproduciblity
To reproduce the analysis:  

- Install all prerequisites software.
- Clone the repository; Positron is recommended for this purpose.
- Run the following in an R terminal to download all packages:
```{r}
#| eval: False
renv::restore()
```

- Source each code file to perform all analyses:
```{r}
#| eval: False
source(here::here("r/01_load_expression.R"))
source(here::here("r/02.R"))
source(here::here("r/03_convert_dds_to_eset.R"))
source(here::here("r/04_gsva_01_run.R"))
source(here::here("r/04_gsva_02_heatmap.R"))
source(here::here("r/04_gsva_03_heatmapfig2.R"))
source(here::here("r/04_gsva_04_volcano3d.R"))
source(here::here("r/04_gsva_05_volcano3d_interactionterm.R"))
source(here::here("r/05_postgsva_heat.R"))
source(here::here("r/05_postgsva_volcano.R"))
```

- Render the figures in a shell terminal:
```
quarto render quarto
```